---
title: "My Test R Markdown"
author: "AA"
date: "31/05/2020"
output: github_document
---
The dataset is publicly available at:
combined.csv: https://data.world/dataquest/nyc-schools-data/workspace/file?filename=combined.csv
NYC school survey data for 2011: https://data.cityofnewyork.us/Education/2011-NYC-School-Survey/mnz3-dyi8

We will try to answer the following questions:

Do student, teacher, and parent perceptions of NYC school quality appear to be related to demographic and academic success metrics?

Do students, teachers, and parents have similar perceptions of NYC school quality?


First, let's load the required libraries:

```{r}
library(readr)
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(tidyr)

```

Let's import the data that we cleaned from the previous courses.

```{r}
combined <- read_csv("combined.csv")

```

Next, we'll import the survey data. The txt survey data is separated by tabs so we will use read_tsv() from the readr library to import the files masterfile11_gened_final.txt and masterfile11_d75_final.txt

```{r}
masterfile1_gened <- read_tsv("masterfile11_gened_final.txt")
masterfile1_d75 <- read_tsv("masterfile11_d75_final.txt")
```


Let's check out the data that we've imported:


```{r}
head(masterfile1_gened,5)
head(masterfile1_d75,5)
```